A New Metropolis-Hastings Test for Fast Minibatch MCMC Inference and Optimization

### 2016-05-16 nips_2016.tex
clean the parts before the experriments

In this section, we use three experiments to reveal the benefits of our mini-batch MH testing. 
\subsection{Mixture of Gaussians}\label{ssec:gaussians}

@@

\section{Neural Network Experiment Details}\label{app:nnet}

>>>>

In this section, we use three experiments to reveal the benefits of our mini-batch MH testing. For the first experiment, we illustrate that our mini-batch MH testing can 
\subsection{Mixture of Gaussians}\label{ssec:gaussians}

@@

We applied our mini-batch Metropolis Hastings algorithm to a Bayesian logistic regression model,
338 comparing with the adaptive sampling method. We tested both our method and the adaptive sampling
339 method using a random walk proposer $q(\theta \mid \theta_t) = N (\theta_t, \sigma^2)$. Since the random walk proposer does random walk
340 not contain any information about the target distribution, it only relies on the Metropolis Hastings
341 test to converge to the correct distribution. Therefore, random walk proposer is the ideal choice for
342 illustrating our algorithm and comparing with the adaptive sampling method.
\section{Neural Network Experiment Details}\label{app:nnet}
